\vspace{-0.25em}\thetitle

### 2009-07-29 paper.tex
...

As better point-measure of the quality of predictors, we propose the maximum vertical distance between its p-value \caps{CDF} and the ideal.
This is equivalent to choosing the worst possible predetermined significance level for each predictor and evaluating it at that level.
Under this measure, predictors cannot ``hide'' their errors by shifting them around the p-value range.
The maximum vertical difference from the ideal for each predictor is shown in \Figure{cdf} with vertical bars.
This is the the overall error rate of the predictor.
The success rate is the complement of the error rate.
\Figure{success-rates} shows the success rates of various predictions across the six data sets.

\begin{figure}[!b]
\vspace{-2em}
\begin{center}
\includegraphics[width=3.5in]{pred_stats}
\caption{Success rates of various prediction methods.}
\fig{success-rates}
\end{center}
\vspace{-1em}
\end{figure}

@@

\begin{figure*}[t]
\begin{center}
\hfill
\subfloat[Packet count: accuracy]{%
\includegraphics[width=2.1in]{pkts_accuracy}}\hfill
\subfloat[Packet count: uncertainty reduction]{%
\includegraphics[width=2.1in]{pkts_certainty}}\hfill
\subfloat[Packet count: prediction entropy]{%
\includegraphics[width=2.1in]{pkts_entropy}}\hfill
\caption{Packet count prediction accuracy, uncertainty reduction and entropy.}
\fig{packets-accuracy}
\end{center}
\vspace{-2em}
\end{figure*}

>>>>

As a better point-measure of the quality of predictors, we propose the maximum vertical distance between its p-value \caps{CDF} and the ideal.
This is equivalent to choosing the worst possible predetermined significance level for each predictor and evaluating it at that level.
Under this measure, predictors cannot ``hide'' their errors by shifting them around the p-value range.
The maximum vertical difference from the ideal for each predictor is shown in \Figure{cdf} with vertical bars.
This is the the overall error rate of the predictor.
The success rate is the complement of the error rate.
\Figure{success-rates} shows the success rates of various predictions across the six data sets.

\begin{figure}[!b]
\vspace{-1em}
\begin{center}
\includegraphics[width=3.5in]{pred_stats}
\caption{Success rates of various prediction methods.}
\fig{success-rates}
\end{center}
\vspace{-0.9em}
\end{figure}

@@

\begin{figure*}[t]
\vspace{-1em}
\begin{center}
\subfloat[Packet count: accuracy]{%
\includegraphics[width=2.1in]{pkts_accuracy}}
\subfloat[Packet count: uncertainty reduction]{%
\includegraphics[width=2.1in]{pkts_certainty}}
\subfloat[Packet count: prediction entropy]{%
\includegraphics[width=2.1in]{pkts_entropy}}
\caption{Packet count predictions: accuracy, uncertainty reduction, and entropy.}
\fig{packets-accuracy}
\end{center}
\vspace{-2em}
\end{figure*}

Next we turn to the evaluation of packet counts predictions.
Here we cannot use the K-S test:
although we have a predicted distribution of possible packet counts, we have only one value to compare it to---the actual number of packets.
The K-S test is useless for samples of fewer than three values---it cannot invalidate any outcome.
Instead we use the predicted distributions themselves to yield p-values for each packet count.
We compute how ``extreme'' each observed packet count value is according to the predicted distribution of packet count values:
that is, what fraction of the distribution is as large or larger than the observed value.
If the predictions are accurate, then these ``p-values'' should be uniformly distributed.

Accuracy alone is insufficient, however:
guessing the mean distribution of packet counts yields a perfectly accurate predictor according to the same criterion.
What we want, however, is to remain accurate but become more certain about the packet count.
